---
title: "MiWaves MRT Analyses Results"
output: pdf_document
geometry: margin=2cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

```
# 1. Primary Aims Analysis (Part 1) with Proximal Cannabis Use Outcome 
  
## Frequencies of Baseline Covariates

Firstly, there are two baseline records for three IDs. For these three IDs, the second baseline record is retained. The two baseline submissions are likely due to the survey timing out and participants re-submitting. 
  
1.)  *CANN_IMPORTANCE_BL*: "Right now, how important is it to you to cut back your cannabis use?" Response: 0-10 likert scale: 0=Not at all, 10=Very
  
Other options: 
  
-  *CANN_LIKELY_BL*: "Right now, how likely are you to cut back your use of cannabis or cannabis products?" Response: scale of 0=Not at all - 10=Very
  
-  *CANN_CONF_BL*: "How confident are you that you could cut back your use of cannabis or cannabis products if you wanted to?" Response: scale of 0=Not at all - 10=Very
  
2.)  *CANNHOURS_BL*: "During the past month, how many hours, on an average day, did you use cannabis?" Response: Drop down selection 0-24
  
3.)  *CANNWAKE_BL*: "During the past month, how soon did you typically use any cannabis products after you woke up for the day?" Response: 1=Within 5 minutes, 2=6-30 minutes, 3=31 minutes to almost 1 hour, 4=1 to almost 2 hours, 5=2 to almost 4 hours, 6=4 or more hours
  
Other options:   
  
-  *CANNDAYS_BL*: "How many days in the past month have you used cannabis?" Response: Drop down selection 0-31
  
-  *CANNMONTH_BL*: "In the past month, how many times per day did you use cannabis?" Response: Drop down selection 0-24
  
*Note*: If *CANNDAYS_BL*>0, then displays *CANNHOURS_BL*, *CANNWAKE_BL*, *CANNMONTH_BL*, *CANN_IMPORTANCE_BL*, *CANN_LIKELY_BL*, and *CANN_CONF_BL*. 
  
   
```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(kableExtra)

outdir<-"~/output"
proc_dat <- "//maize.umhsnas.med.umich.edu/Psychiatry/Restricted/MiWaves/Pilot/Processed Data/"

# load R datafile
load(file = paste0(proc_dat,"miwaves_analysis_dataset_w_bl.Rdata"))

prim_dat <- prim_dat %>%
  # restrict to participants with at least 3 completed EMAs
  filter(num_emas_l >= 3) %>%
  # remove observations where the randomization information is missing
  filter(missing_rand != 1) %>%
  #filter(completed_ema_l==1)
  filter(!is.na(prop_awakeuse))
#filter(is.na(prop_awakeuse) & !is.na(prop_use_unadj_l))
  
prim_dat <- prim_dat %>%
  # restrict to IDs with completed baseline survey
  filter( !(is.na(completed_baseline))) %>%
  mutate(cann_importance_bl= ifelse(is.na(cann_importance_bl),0,cann_importance_bl),
         cannhours_bl= ifelse(is.na(cannhours_bl),0,cannhours_bl),
         cannwake_bl= ifelse(is.na(cannwake_bl),0,cannwake_bl))

cann_importance_bl_freq <- prim_dat %>%
  select(id,cann_importance_bl)%>%
  distinct(id,cann_importance_bl)%>%
  mutate(flag=1)%>%
  group_by(cann_importance_bl) %>%
  # denominator is 120 IDs in analysis sample
  summarise( count = sum(flag,na.rm=T),
             percent = 100*round((count / 120), 3))%>%
  ungroup()

cann_importance_bl_freq %>%
  kable(
    align = "c", caption = "Frequency of baseline variable cannabis importance $(N=120 EAs)$")%>%
  kable_classic(full_width = F)

cannhours_bl_freq <- prim_dat %>%
  select(id,cannhours_bl)%>%
  distinct(id,cannhours_bl)%>%
  mutate(flag=1)%>%
  group_by(cannhours_bl) %>%
  # denominator is 120 IDs in analysis sample
  summarise( count = sum(flag,na.rm=T),
             percent = 100*round((count / 120), 3))%>%
  ungroup()

cannhours_bl_freq %>%
  kable(
    align = "c", caption = "Frequency of baseline variable cannabis hours $(N=120 EAs)$")%>%
  kable_classic(full_width = F)

cannwake_bl_freq <- prim_dat %>%
  select(id,cannwake_bl)%>%
  distinct(id,cannwake_bl)%>%
  mutate(flag=1)%>%
  group_by(cannwake_bl) %>%
  # denominator is 120 IDs in analysis sample
  summarise( count = sum(flag,na.rm=T),
             percent = 100*round((count / 120), 3))%>%
  ungroup()

cannwake_bl_freq %>%
   kable(
     align = "c", caption = "Frequency of baseline variable cannabis after waking $(N=120 EAs)$")%>%
   kable_classic(full_width = F)
```

## Distribution of Self-Reported Proportion of Waking Hours with Cannabis Use by Baseline Candidate Moderators

```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)


prim_dat$Action = factor(prim_dat$intmessage_randassignment,levels=c(0,1),labels=c("No Message","Yes Message"))

colors <- c("#dc0000ff","#00a087ff")
plot_violin <- function(dat, category_lbl, x_axis_lbl, metric, metric_lbl, low_limit, high_limit) {
  ggplot(dat, aes(x = get(category_lbl), y = get(metric), 
         color = Action, fill=Action)) +
    geom_violin(alpha = 0.2) +
    geom_boxplot(width = 0.2, position = position_dodge(width=0.9), 
                 outlier.shape = NA, alpha = 0.3) +
    theme_minimal() +
    scale_y_continuous(breaks=scales::breaks_pretty(n = 10), 
                       limits=c(low_limit, high_limit)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) + 
    scale_x_discrete(labels=xlabs) +
    labs(y = metric_lbl, x = x_axis_lbl) +
    theme(legend.title = element_blank(),
          legend.position = "bottom",
          text=element_text(size=11))
}

# Proportion of Awake Hours with Self-Reported Cannabis Use
xlabs <- paste(c("Male","Female"),"\n(n=",table(prim_dat$sex_lbl),")",sep="")
p1 <-plot_violin(dat=prim_dat, category_lbl="sex_lbl", x_axis_lbl="Biological Sex", metric="prop_awakeuse",metric_lbl="Self-Reported Proportion of Waking Hours Using Cannabis", low_limit = 0.0, high_limit=1)
print(p1)

xlabs <- paste(c("Asian","Black/African American", "> 1 race","Other", "Unknown", "White"),"\n(n=",table(prim_dat$race_lbl),")",sep="")
p2 <-plot_violin(dat=prim_dat, category_lbl="race_lbl", x_axis_lbl="Self-Reported Race", metric="prop_awakeuse",metric_lbl="Self-Reported Proportion of Waking Hours Using Cannabis", low_limit = 0.0, high_limit=1)
print(p2)

xlabs <- paste(c("Hispanic or Latino","Not Hispanic or Latino"),"\n(n=",table(prim_dat$ethnicity_lbl),")",sep="")
p3 <-plot_violin(dat=prim_dat, category_lbl="ethnicity_lbl", x_axis_lbl="Self-Reported Ethnicity", metric="prop_awakeuse",metric_lbl="Self-Reported Proportion of Waking Hours Using Cannabis", low_limit = 0.0, high_limit=1)
print(p3)


```

\newpage
  
## *Preliminary* Causal Excursion Effect Estimates
  
**Research Question 1**: Examine whether, on average, there is a proximal effect of delivering an intervention message on proximal cannabis use   
  
**Proximal outcome ($Y_{i,t+1}$)**: Proportion of waking hours with self-reported cannabis use (0-1, treated as continuous)  
    
**Treatment indicator ($A_{i,t}$)**: Binary (1=Yes message, 0=No message)  
  
**Covariates**:  
  
-  time of day – binary (AM=0, PM=1),  
  
-  day of the week  – binary (weekday=1, weekend [Fri-Sun]=0),  
  
-  prior cannabis use – proportion of waking hours averaged over past 4 decision points (i.e., approximately 48 hours), 
  
-  prior intervention engagement – score that ranges from 0-3 averaged over past 6 decision points (i.e., approximately 72 hours),  
  
-  baseline motivation to change – importance of cutting back cannabis use on a scale from 0 (Not at all) to 10 (Very) at time of baseline survey,  
  
-  baseline cannabis use – self-reported average hours of cannabis use in prior day (range: 0-24), during the past month, and 
  
-  baseline time to cannabis use - self-reported time to cannabis use, since awaking (1=Within 5 minutes, 2=6-30 minutes, 3=31 minutes to almost 1 hour, 4=1 to almost 2 hours, 5=2 to almost 4 hours, 6=4 or more hours), during the past month.  
  
**Candidate Moderators**: We explore whether the effect of the intervention message on proximal cannabis use varries by each of the candidate moderators listed below. 
  
1. *timeofday*: time of day – binary (AM=1, PM=0),
  
2. *interact_A_message*: interaction type A message vs. no message – binary (interaction type A message=1, no message=0),  
  
- 2.2. *interact_B_message*: interaction type B message vs. no message – binary (interaction type B message=1, no message=0),  
  
- 2.3. *interact_C_message*: interaction type C message vs. no message – binary (interaction type C message=1, no message=0),
  
3. *prop_awakeuse_prior*: prior cannabis use – operationalized the same as the proximal outcome, at the prior decision point,
  
- 3.2. *cov_prop_awakeuse_48hrs*: prior cannabis use over the past 4 decision points,
  
4. *wks_since_interv_start*: time since under treatment (i.e., since intervention start) in weeks,
  
5. *week_day_binary1*: day of the week – binary (weekday=1, weekend [Fri-Sun]=0),
  
6. *prior_interv_engag*: prior intervention engagement – operationalized the same as the proximal outcome, at the prior decision point,
  
- 6.2. *cov_interv_engag_72hrs*: over past 6 decision points,
  
7. *prior_sent_message*: prior delivery of a message – binary (yes message=1, no message=0), at the prior decision point,
  
- 7.2. *prior_sent_messages_48hrs*: number of messages sent over past 4 decision points,
  
8. *short_message*: short message vs. no message – binary (short message=1, no message=0),  
  
- 8.2. *long_message*: long message vs. no message - binary (long message=1, no message=0),  
  
9. *sex*: baseline demographic of biological sex (female=1,male=0),  
  
10. *race*: baseline demographic of race (white=1, 0=non-white),   
  
11. *ethnicity*: baseline demographic of ethnicity (1=not hispanic or latino, 0=hispanic or latino),
  
12. *canndays_bl*: baseline cannabis use severity that is the number of days used cannabis in past month (range: 0-31), which reflects cannabis use frequency, 
  
- 12.2. *dsmsc_tot_bl*: baseline cannabis use severity that is the count of number of symptoms endorsed (range: 0-11), which reflects diagnostic severity,  
  
13. *cann_importance_bl*: baseline motivation to change that is the importance of cutting back cannabis use on a scale from 0 (Not at all) to 10 (Very) at time of baseline survey, and 
  
14. *phq2_tot_bl*: baseline mental health, which is the sum across two item scale PHQ-2 ("Over the last two weeks, how often have you been bothered by any of the following problems? Little interest or pleasure in doing things" and "Over the last two weeks, how often have you been bothered by any of the following problems? Feeling down, depressed, or hopeless" with response values of 0=Not at all, 1= Several days, 2=More than half the days, and 3=Nearly every day).

```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(kableExtra)
library(MRTAnalysis)
library(gt)

df <- prim_dat %>%
  arrange(id,decision_point) %>%
  rename(actioni=intmessage_randassignment, probi= intmessage_randprob, 
         prior_interv_engag = interv_engagement) %>%
  mutate(timeofday = ifelse(morning==1,0,1),
         message_interaction_type = ifelse(message_type == "A",1,
                                      ifelse(message_type=="B",2,
                                             ifelse(message_type=="C",3,1))),
         message_interaction_type = as.factor(message_interaction_type),
         message_length = ifelse(is.na(message_length),"Not applicable",message_length),
         # create time since under treatment (i.e., since study start) in weeks
         wks_since_interv_start = case_when(day<=7 ~ 1,
                                              (day>7) & (day<=14) ~ 2,
                                              (day>14) & (day<=21) ~ 3,
                                              (day>21) & (day<=30) ~ 4)
         
        ) %>%
  group_by(id) %>%
  mutate(# create prior sending of a message candidate moderator
         prior_sent_message = lag(actioni)
         ) %>%
  ungroup() %>%
  filter(!is.na(cov_prop_awakeuse_48hrs))

        
#print(paste0("Sample size: ",nrow(df)))

r <- list()

fit_wocov <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~1
)

r[[1]] <- summary(fit_wocov)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (no covars)")
  
fit_wcov <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~ cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[2]] <- summary(fit_wcov)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (with covars)")

fit1 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~timeofday,
    control_formula = ~ cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[3]] <- summary(fit1)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 1")

# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_temp <- df %>% 
  # restrict to interaction A type message and no message
  filter(!(message_type %in% c("B","C"))) %>%
  mutate(interact_A_message = ifelse(actioni==0,0,1))
fit2 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "interact_A_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[4]] <- summary(fit2)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2")

# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_temp <- df %>% 
  # restrict to interaction B type message and no message
  filter(!(message_type %in% c("A","C"))) %>%
  mutate(interact_B_message = ifelse(actioni==0,0,1))

fit2b <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "interact_B_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[5]] <- summary(fit2b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2.2")


# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_temp <- df %>% 
  # restrict to interaction C type message and no message
  filter(!(message_type %in% c("A","B"))) %>%
  mutate(interact_C_message = ifelse(actioni==0,0,1))

fit2c <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "interact_C_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[6]] <- summary(fit2c)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2.3")


df_temp <- df %>% filter(!is.na(prop_awakeuse_prior)) 
fit3 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prop_awakeuse_prior,
    control_formula = ~prop_awakeuse_prior + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[7]] <- summary(fit3)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 3")


fit3b <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_prop_awakeuse_48hrs,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[8]] <- summary(fit3b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 3.2")


fit4 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~wks_since_interv_start,
    control_formula = ~wks_since_interv_start + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[9]] <- summary(fit4)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 4")

fit5 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~week_day_binary,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[10]] <- summary(fit5)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 5")

df_temp <- df %>% filter(!is.na(prior_interv_engag)) 
fit6 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_interv_engag,
    control_formula = ~cov_prop_awakeuse_48hrs + prior_interv_engag  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[11]] <- summary(fit6)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 6")

fit6b <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_interv_engag_72hrs,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[12]] <- summary(fit6b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 6.2")

df_temp <- df %>% filter(!is.na(prior_sent_message)) 
fit7 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_sent_message,
    control_formula = ~prior_sent_message + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[13]] <- summary(fit7)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7")

df_temp <- df %>% filter(!is.na(prior_sent_messages_48hrs)) 
fit7b <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_sent_messages_48hrs,
    control_formula = ~prior_sent_messages_48hrs + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[14]] <- summary(fit7b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7.2")

# short vs no message
df_temp <- df %>%
  # restrict to short message and no message
  filter(message_length!="Long") %>%
  mutate(short_message = ifelse(actioni==0,0,1))

fit8 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "short_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[15]] <- summary(fit8)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 8")


# # long vs no message
df_temp <- df %>%
  # restrict to long message and no message
  filter(message_length!="Short") %>%
  mutate(long_message = ifelse(actioni==0,0,1))

fit8b <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "long_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[16]] <- summary(fit8b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 8.2")


fit9 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~sex,
    control_formula = ~sex + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[17]] <- summary(fit9)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 9")

fit10 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~white_race,
    control_formula = ~white_race + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[18]] <- summary(fit10)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 10")


fit11 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~ethnicity,
    control_formula = ~ethnicity + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[19]] <- summary(fit11)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 11")

fit12 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~canndays_bl,
    control_formula = ~ canndays_bl + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[20]] <- summary(fit12)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 12")

fit12b <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~dsmsc_tot_bl,
    control_formula = ~dsmsc_tot_bl + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[21]] <- summary(fit12b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 12.2")

fit13 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_importance_bl,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[22]] <- summary(fit13)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 13")


fit14 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~phq2_tot_bl,
    control_formula = ~phq2_tot_bl + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[23]] <- summary(fit14)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14")


res <- r %>% 
  map_df(bind_rows) %>% 
  select(model, everything()) %>%
  dplyr::mutate(model_num = gsub("Moderation Effect Model ","",model),
         model_num = ifelse(model=="Main Effect Model (no covars)","0",
                            ifelse(model=="Main Effect Model (with covars)","0.5",model_num)),
         model_num = as.numeric(model_num)
  )%>%
  dplyr::arrange(model_num) 

# create table with output
res_table <- function(res){
    res %>%
      mutate(term = str_replace(term, "\\(Intercept\\)", "Intercept")) %>%
      rename(Term = term)%>%
      select(-c(model,model_num)) %>%
      kableExtra::kbl(booktabs = TRUE, 
                      longtable = TRUE,
                      digits=3,
                      format = "latex",
                      caption = NULL) %>%
      kableExtra::kable_styling(
        latex_options = c("striped", "hold_position", "repeat_header"),
        font_size = 10
        #full_width = TRUE
      ) %>%
      kableExtra::pack_rows(index = table(fct_inorder(res$model))) %>%
      kableExtra::column_spec(1, width = "4.7cm") %>%
      kableExtra::column_spec(7, width = "1cm") %>%
      kableExtra::column_spec(8, width = "1cm") %>%
      kableExtra::footnote(
        general = "baseline cannabis use, and baseline time to cannabis use.", general_title = "", footnote_as_chunk = T
      ) %>%
      kableExtra::footnote(
        general = "prior cannabis use, prior intervention engagement, baseline motivation to change,",
        general_title = "", footnote_as_chunk = T
      )%>%
      kableExtra::footnote(
        general = "Moderation Effect Models include the covariates: time of day, day of week,", general_title = "", footnote_as_chunk = T
      ) %>%
      kableExtra::footnote(
        general = "Notes: Standard errors are not yet adjusted to account for RL uncertainty.", general_title = "", footnote_as_chunk = T
      ) 
}

res_table(res)
```


# 2. Primary Aims Analysis (Part 2) with Proximal Intervention Engagement Outcome
    
## *Preliminary* Causal Excursion Effect Estimates
  
**Research Question 1**: Investigate whether, on average, there is a proximal effect of delivering an intervention message on proximal intervention engagement.   
  
**Proximal outcome ($Y_{i,t+1}$)**: Intervention engagement (discrete: 0-3, treated as continuous)  
    
**Treatment indicator ($A_{i,t}$)**: Binary (1=Yes message, 0=No message)  
  
**Covariates**:  
  
-  time of day – binary (AM=0, PM=1),  
  
-  day of the week  – binary (weekday=1, weekend [Fri-Sun]=0),  
  
-  prior intervention engagement – score that ranges from 0-3 averaged over past 6 decision points (i.e., approximately 72 hours), 
  
-  prior human-touch engagement – binary (1=yes, 0=no) for any email, text, or phone call made by study staff (after 72 hours, 120 hours, and 168 hours [1 week])  over past 4 decision points (i.e., approximately 48 hours).  
  

```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(kableExtra)
library(MRTAnalysis)
library(gt)

df <- prim_dat %>%
  arrange(id,decision_point) %>%
  rename(actioni=intmessage_randassignment, probi= intmessage_randprob, 
         prior_interv_engag = interv_engagement) %>%
  mutate(timeofday = ifelse(morning==1,0,1),
         message_interaction_type = ifelse(message_type == "A",1,
                                      ifelse(message_type=="B",2,
                                             ifelse(message_type=="C",3,1))),
         message_interaction_type = as.factor(message_interaction_type),
         message_length = ifelse(is.na(message_length),"Not applicable",message_length),
         # create time since under treatment (i.e., since study start) in weeks
         wks_since_interv_start = case_when(day<=7 ~ 1,
                                              (day>7) & (day<=14) ~ 2,
                                              (day>14) & (day<=21) ~ 3,
                                              (day>21) & (day<=30) ~ 4)
         
        ) %>%
  group_by(id) %>%
  mutate(# create prior sending of a message candidate moderator
         prior_sent_message = lag(actioni)
         ) %>%
  ungroup()
  #filter(!is.na(cov_prop_awakeuse_48hrs))

        
#print(paste0("Sample size: ",nrow(df)))

r <- list()

fit_wocov <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~1
)

r[[1]] <- summary(fit_wocov)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (no covars)")
  
fit_wcov <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~ timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[2]] <- summary(fit_wcov)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (with covars)")

res <- r %>% 
  map_df(bind_rows) %>% 
  select(model, everything()) %>%
  dplyr::mutate(model_num = gsub("Moderation Effect Model ","",model),
         model_num = ifelse(model=="Main Effect Model (no covars)","0",
                            ifelse(model=="Main Effect Model (with covars)","0.5",model_num)),
         model_num = as.numeric(model_num)
  )%>%
  dplyr::arrange(model_num) 

# create table with output
res_table <- function(res){
    res %>%
      mutate(term = str_replace(term, "\\(Intercept\\)", "Intercept")) %>%
      rename(Term = term)%>%
      select(-c(model,model_num)) %>%
      kableExtra::kbl(booktabs = TRUE, 
                      longtable = TRUE,
                      digits=3,
                      format = "latex",
                      caption = NULL) %>%
      kableExtra::kable_styling(
        latex_options = c("striped", "hold_position", "repeat_header"),
        font_size = 10
        #full_width = TRUE
      ) %>%
      kableExtra::pack_rows(index = table(fct_inorder(res$model))) %>%
      kableExtra::column_spec(1, width = "4.7cm") %>%
      kableExtra::column_spec(7, width = "1cm") %>%
      kableExtra::column_spec(8, width = "1cm") %>%
      kableExtra::footnote(
        general = "prior intervention engagement, and prior human-touch engagement.",
        general_title = "", footnote_as_chunk = T
      )%>%
      kableExtra::footnote(
        general = "Model with covariates adjusts for the following: time of day, day of week,", general_title = "", footnote_as_chunk = T
      ) %>%
      kableExtra::footnote(
        general = "Notes: Standard errors are not yet adjusted to account for RL uncertainty.", general_title = "", footnote_as_chunk = T
      ) 
}

res_table(res)
```