---
title: "MiWaves MRT Analyses Results"
output: pdf_document
geometry: margin=2cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

```
# 1. Primary Aims Analysis (Part 1) with Proximal Cannabis Use Outcome 
  
## Frequencies of Baseline Covariates

Firstly, there are two baseline records for three IDs. For these three IDs, the second baseline record is retained. The two baseline submissions are likely due to the survey timing out and participants re-submitting. 
  
1.)  *CANN_IMPORTANCE_BL*: "Right now, how important is it to you to cut back your cannabis use?" Response: 0-10 likert scale: 0=Not at all, 10=Very
  
Other options: 
  
-  *CANN_LIKELY_BL*: "Right now, how likely are you to cut back your use of cannabis or cannabis products?" Response: scale of 0=Not at all - 10=Very
  
-  *CANN_CONF_BL*: "How confident are you that you could cut back your use of cannabis or cannabis products if you wanted to?" Response: scale of 0=Not at all - 10=Very
  
2.)  *CANNHOURS_BL*: "During the past month, how many hours, on an average day, did you use cannabis?" Response: Drop down selection 0-24
  
3.)  *CANNWAKE_BL*: "During the past month, how soon did you typically use any cannabis products after you woke up for the day?" Response: 1=Within 5 minutes, 2=6-30 minutes, 3=31 minutes to almost 1 hour, 4=1 to almost 2 hours, 5=2 to almost 4 hours, 6=4 or more hours
  
Other options:   
  
-  *CANNDAYS_BL*: "How many days in the past month have you used cannabis?" Response: Drop down selection 0-31
  
-  *CANNMONTH_BL*: "In the past month, how many times per day did you use cannabis?" Response: Drop down selection 0-24
  
*Note*: If *CANNDAYS_BL*>0, then displays *CANNHOURS_BL*, *CANNWAKE_BL*, *CANNMONTH_BL*, *CANN_IMPORTANCE_BL*, *CANN_LIKELY_BL*, and *CANN_CONF_BL*. 
  
   
```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(kableExtra)

outdir<-"~/output"
proc_dat <- "//maize.umhsnas.med.umich.edu/Psychiatry/Restricted/MiWaves/Pilot/Processed Data/"

# load R datafile
 load(file = paste0(proc_dat,"miwaves_analysis_dataset_w_bl.Rdata"))

full_dat <- prim_dat %>%
  dplyr::arrange(id,decision_point) %>%
  # restrict to IDs with completed baseline survey
  dplyr::filter( !(is.na(completed_baseline))) %>%
  dplyr::mutate(cann_importance_bl= ifelse(is.na(cann_importance_bl),0,cann_importance_bl),
         cann_likely_bl= ifelse(is.na(cann_likely_bl),0,cann_likely_bl),
         cann_conf_bl= ifelse(is.na(cann_conf_bl),0,cann_conf_bl),
         cannhours_bl= ifelse(is.na(cannhours_bl),0,cannhours_bl),
         cannwake_bl= ifelse(is.na(cannwake_bl),0,cannwake_bl),
         high_cann_importance_bl = ifelse(cann_importance_bl < 5, 0,
                                          ifelse(cann_importance_bl >= 5, 1, 999)),
         high_cann_importance_bl = factor(high_cann_importance_bl, levels=c(0,1)),
         sex = factor(sex, levels=c(1,2), labels=c("Male", "Female")),
         male_sex = ifelse(sex=="Male", 1, 0),
         male_sex = factor(male_sex),
         white_race = factor(white_race),
         ethnicity = factor(ethnicity, levels=c(1,2), labels=c("Hispanic or Latino", "Not Hispanic or Latino")),
         hispanic_ethn = ifelse(ethnicity=="Hispanic or Latino", 1, 0),
         hispanic_ethn = factor(hispanic_ethn)) %>%
  dplyr::rename(actioni=intmessage_randassignment, probi= intmessage_randprob, 
         prior_interv_engag = interv_engagement) %>%
  dplyr::mutate(timeofday = ifelse(morning==1,0,1),
                timeofday = factor(timeofday, levels=c(0,1), labels=c("AM", "PM")),
                week_day_binary = factor(week_day_binary),
         message_interaction_type = ifelse(message_type == "A",1,
                                      ifelse(message_type=="B",2,
                                             ifelse(message_type=="C",3,1))),
         message_interaction_type = as.factor(message_interaction_type),
         message_length = ifelse(is.na(message_length),"Not applicable",message_length),
         # create time since under treatment (i.e., since study start) in weeks
         wks_since_interv_start = case_when(day<=7              ~ 1,
                                           (day>7) & (day<=14)  ~ 2,
                                           (day>14) & (day<=21) ~ 3,
                                           (day>21) & (day<=30) ~ 4),
         after_day15 = case_when(day<=15 ~ 0,
                                 day>15  ~ 1),
         after_day15 = factor(after_day15)
        ) %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(# create prior sending of a message candidate moderator
         prior_sent_message = lag(actioni),
         log_awakeuse_offs = prop_awakeuse + 0.001,
         log_awakeuse = log(log_awakeuse_offs),
         logit_awakeuse = log((log_awakeuse_offs)/(1-(log_awakeuse_offs)))
         
         ) %>%
  dplyr::ungroup() 

df <- full_dat %>%
  # restrict to participants with at least 3 completed EMAs
  dplyr::filter(num_emas_l >= 3) %>%
  # remove observations where the randomization information is missing
  dplyr::filter(missing_rand != 1) %>%
  dplyr::filter(!is.na(prop_awakeuse))%>%
  dplyr::filter(!is.na(cov_prop_awakeuse_48hrs))
  

cann_importance_bl_freq <- df %>%
  select(id,cann_importance_bl)%>%
  distinct(id,cann_importance_bl)%>%
  mutate(flag=1)%>%
  group_by(cann_importance_bl) %>%
  # denominator is 120 IDs in analysis sample
  summarise( count = sum(flag,na.rm=T),
             percent = 100*round((count / 120), 3))%>%
  ungroup()

cann_importance_bl_freq %>%
  kable(
    align = "c", caption = "Frequency of baseline variable cannabis importance $(N=120 EAs)$")%>%
  kable_classic(full_width = F)


high_cann_importance_bl_freq <- df %>%
  select(id,high_cann_importance_bl)%>%
  distinct(id,high_cann_importance_bl)%>%
  mutate(flag=1)%>%
  group_by(high_cann_importance_bl) %>%
  # denominator is 120 IDs in analysis sample
  summarise( count = sum(flag,na.rm=T),
             percent = 100*round((count / 120), 3))%>%
  ungroup()

high_cann_importance_bl_freq %>%
  kable(
    align = "c", caption = "Frequency of baseline dichotomized variable high cannabis importance $(N=120 EAs)$")%>%
  kable_classic(full_width = F)

cann_likely_bl_freq <- df %>%
  select(id,cann_likely_bl)%>%
  distinct(id,cann_likely_bl)%>%
  mutate(flag=1)%>%
  group_by(cann_likely_bl) %>%
  # denominator is 120 IDs in analysis sample
  summarise( count = sum(flag,na.rm=T),
             percent = 100*round((count / 120), 3))%>%
  ungroup()

cann_likely_bl_freq %>%
  kable(
    align = "c", caption = "Frequency of baseline variable cannabis likely $(N=120 EAs)$")%>%
  kable_classic(full_width = F)

cann_conf_bl_freq <- df %>%
  select(id,cann_conf_bl)%>%
  distinct(id,cann_conf_bl)%>%
  mutate(flag=1)%>%
  group_by(cann_conf_bl) %>%
  # denominator is 120 IDs in analysis sample
  summarise( count = sum(flag,na.rm=T),
             percent = 100*round((count / 120), 3))%>%
  ungroup()

cann_conf_bl_freq %>%
  kable(
    align = "c", caption = "Frequency of baseline variable cannabis confidence $(N=120 EAs)$")%>%
  kable_classic(full_width = F)

cannhours_bl_freq <- df %>%
  select(id,cannhours_bl)%>%
  distinct(id,cannhours_bl)%>%
  mutate(flag=1)%>%
  group_by(cannhours_bl) %>%
  # denominator is 120 IDs in analysis sample
  summarise( count = sum(flag,na.rm=T),
             percent = 100*round((count / 120), 3))%>%
  ungroup()

cannhours_bl_freq %>%
  kable(
    align = "c", caption = "Frequency of baseline variable cannabis hours $(N=120 EAs)$")%>%
  kable_classic(full_width = F)

cannwake_bl_freq <- df %>%
  select(id,cannwake_bl)%>%
  distinct(id,cannwake_bl)%>%
  mutate(flag=1)%>%
  group_by(cannwake_bl) %>%
  # denominator is 120 IDs in analysis sample
  summarise( count = sum(flag,na.rm=T),
             percent = 100*round((count / 120), 3))%>%
  ungroup()

cannwake_bl_freq %>%
   kable(
     align = "c", caption = "Frequency of baseline variable cannabis after waking $(N=120 EAs)$")%>%
   kable_classic(full_width = F)
```

## Distribution of Self-Reported Proportion of Waking Hours with Cannabis Use by Baseline Candidate Moderators

```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)


df$Action = factor(df$actioni,levels=c(0,1),labels=c("No Message","Yes Message"))

colors <- c("#dc0000ff","#00a087ff")
plot_violin <- function(dat, category_lbl, x_axis_lbl, metric, metric_lbl, low_limit, high_limit) {
  ggplot(dat, aes(x = get(category_lbl), y = get(metric), 
         color = Action, fill=Action)) +
    geom_violin(alpha = 0.2) +
    geom_boxplot(width = 0.2, position = position_dodge(width=0.9), 
                 outlier.shape = NA, alpha = 0.3) +
    theme_minimal() +
    scale_y_continuous(breaks=scales::breaks_pretty(n = 10), 
                       limits=c(low_limit, high_limit)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) + 
    scale_x_discrete(labels=xlabs) +
    labs(y = metric_lbl, x = x_axis_lbl) +
    theme(legend.title = element_blank(),
          legend.position = "bottom",
          text=element_text(size=11))
}

# Proportion of Awake Hours with Self-Reported Cannabis Use
xlabs <- paste(c("Male","Female"),"\n(n=",table(df$sex_lbl),")",sep="")
p1 <-plot_violin(dat=df, category_lbl="sex_lbl", x_axis_lbl="Biological Sex", metric="prop_awakeuse",metric_lbl="Self-Reported Proportion of Waking Hours Using Cannabis", low_limit = 0.0, high_limit=1)
print(p1)

xlabs <- paste(c("Asian","Black/African American", "> 1 race","Other", "Unknown", "White"),"\n(n=",table(df$race_lbl),")",sep="")
p2 <-plot_violin(dat=df, category_lbl="race_lbl", x_axis_lbl="Self-Reported Race", metric="prop_awakeuse",metric_lbl="Self-Reported Proportion of Waking Hours Using Cannabis", low_limit = 0.0, high_limit=1)
print(p2)

xlabs <- paste(c("Hispanic or Latino","Not Hispanic or Latino"),"\n(n=",table(df$ethnicity_lbl),")",sep="")
p3 <-plot_violin(dat=df, category_lbl="ethnicity_lbl", x_axis_lbl="Self-Reported Ethnicity", metric="prop_awakeuse",metric_lbl="Self-Reported Proportion of Waking Hours Using Cannabis", low_limit = 0.0, high_limit=1)
print(p3)


```

\newpage
 
## Overall Distribution of Proximal Outcome 
```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(ggplot2)

h1 <- ggplot(data=df,aes(x=prop_awakeuse)) +
  geom_histogram(alpha=.5) + 
  theme_bw() +
  scale_x_continuous(expand = c(0,0.01)) +
  theme(text = element_text(family = "Helvetica",size = 10)) + 
  ggtitle("") + labs(x = "Proportion of Hours with Cannabis Use", y = "Count of Decision Points")

h2 <- ggplot(data=df,aes(x=log_awakeuse)) +
  geom_histogram(alpha=.5) + 
  theme_bw() +
  #scale_x_continuous(expand = c(0,0.01)) +
  theme(text = element_text(family = "Helvetica",size = 10)) + 
  ggtitle("") + labs(x = "log(p)", y = "Count of Decision Points")

h3 <- ggplot(data=df,aes(x=logit_awakeuse)) +
  geom_histogram(alpha=.5) + 
  theme_bw() +
  #scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  #scale_x_continuous(breaks = seq(1,27,5),
  #                   limits = c(1,27)) +
  #scale_x_continuous(expand = c(0,0.01)) +
  theme(text = element_text(family = "Helvetica",size = 10)) +
        #axis.text.x = element_text(angle = 320)) + 
  ggtitle("") + labs(x = "log(p/(1-p))", y = "Count of Decision Points")

cowplot::plot_grid( 
  h1,
  h2,
  h3
)

```
\newpage
  
## *Preliminary* Causal Excursion Effect Estimates
  
**Research Question 1**: Examine whether, on average, there is a proximal effect of delivering an intervention message on proximal cannabis use   
  
**Proximal outcome ($Y_{i,t+1}$)**: Proportion of waking hours with self-reported cannabis use (0-1, treated as continuous)  
    
**Treatment indicator ($A_{i,t}$)**: Binary (1=Yes message, 0=No message)  
  
**Covariates**:  
  
-  time of day – binary (AM=0, PM=1),  
  
-  day of the week – binary (weekday=1, weekend [Fri-Sun]=0),  
  
-  prior cannabis use – proportion of waking hours averaged over past 4 decision points (i.e., approximately 48 hours), 
  
-  prior intervention engagement – score that ranges from 0-3 averaged over past 6 decision points (i.e., approximately 72 hours),  
  
-  baseline motivation to change – importance of cutting back cannabis use on a scale from 0 (Not at all) to 10 (Very) at time of baseline survey,  
  
-  baseline cannabis use – self-reported average hours of cannabis use in prior day (range: 0-24), during the past month, and 
  
-  baseline time to cannabis use - self-reported time to cannabis use, since awaking (1=Within 5 minutes, 2=6-30 minutes, 3=31 minutes to almost 1 hour, 4=1 to almost 2 hours, 5=2 to almost 4 hours, 6=4 or more hours), during the past month.  
**Research Question 2**: Explore whether the effect of the intervention message on proximal cannabis use varies by each of the candidate moderators listed below.  
  
**Candidate Moderators**:   
  
1. *timeofday*: time of day – binary (AM=0, PM=1),
  
2. *interact_A_message*: interaction type A message vs. no message – binary (interaction type A message=1, no message=0),  
  
- 2.2. *interact_B_message*: interaction type B message vs. no message – binary (interaction type B message=1, no message=0),  
  
- 2.3. *interact_C_message*: interaction type C message vs. no message – binary (interaction type C message=1, no message=0),
  
3. *prop_awakeuse_prior*: prior cannabis use – operationalized the same as the proximal outcome, at the prior decision point,
  
- 3.2. *cov_prop_awakeuse_48hrs*: prior cannabis use over the past 4 decision points,
  
4. *wks_since_interv_start*: time since under treatment (i.e., since intervention start) in weeks,

- 4.2 *after_day15* [a]: time since under treatment (i.e., since intervention start) dichotomized (0=before and including day 15, 1=after day 15),
  
5. *week_day_binary*: day of the week – binary (weekday=1, weekend [Fri-Sun]=0),
  
6. *prior_interv_engag*: prior intervention engagement – operationalized the same as the proximal outcome, at the prior decision point,
  
- 6.2. *cov_interv_engag_72hrs*: over past 6 decision points,
  
7. *prior_sent_message*: prior delivery of a message – binary (yes message=1, no message=0), at the prior decision point,
  
- 7.2. *prior_sent_messages_48hrs*: number of messages sent over past 4 decision points,
  
8. *short_message*: short message vs. no message – binary (short message=1, no message=0),  
  
- 8.2. *long_message*: long message vs. no message - binary (long message=1, no message=0),  
  
9. *male_sex*: baseline demographic of male biological sex (0=female,1=male),  
  
10. *white_race*: baseline demographic of white race (0=not white, 1=white),   
  
11. *hispanic_ethn*: baseline demographic of hispanic or latino ethnicity (0=not hispanic or latino, 1=hispanic or latino),
  
12. *canndays_bl*: baseline cannabis use severity that is the number of days used cannabis in past month (range: 0-31), which reflects cannabis use frequency, 
  
- 12.2. *dsmsc_tot_bl*: baseline cannabis use severity that is the count of number of symptoms endorsed (range: 0-11), which reflects diagnostic severity,  
  
13. *cann_importance_bl*: baseline motivation to change that is the importance of cutting back cannabis use on a scale from 0 (Not at all) to 10 (Very) at time of baseline survey, 
  
- 13.2. *high_cann_importance_bl* [a]: baseline motivation to change - binary (0=low motivation to change [score<5], 1=high motivation to change [score>=5]),
  
- 13.3. *cann_likely_bl* [a]: baseline likelihood to change that is how likely one is to cut back cannabis use on a scale from 0 (Not at all) to 10 (Very) at the time of baseline survey,  
  
- 13.4. *cann_conf_bl* [a]: baseline confidence to change that is how confident one is to cut back cannabis use on a scale from 0 (Not at all) to 10 (Very) at the time of baseline survey, 
  
14. *phq2_tot_bl*: baseline mental health, which is the sum across two item scale PHQ-2 ("Over the last two weeks, how often have you been bothered by any of the following problems? Little interest or pleasure in doing things" and "Over the last two weeks, how often have you been bothered by any of the following problems? Feeling down, depressed, or hopeless" with response values of 0=Not at all, 1= Several days, 2=More than half the days, and 3=Nearly every day).

Notes: All continuous candidate moderators are mean-centered.  
[a] This candidate moderator was included after the list of moderators was formalized.

\newpage
```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(kableExtra)
library(MRTAnalysis)
library(gt)

#print(paste0("Sample size: ",nrow(df)))

# center by grand mean
# specify list of continuous covariates that intend to mean center
vars.standardize <- c("prop_awakeuse_prior","cov_prop_awakeuse_48hrs",
                      "prior_interv_engag","cov_interv_engag_72hrs","prior_sent_messages_48hrs",
                      "canndays_bl","dsmsc_tot_bl",
                      "cann_importance_bl","cann_likely_bl","cann_conf_bl",
                      "phq2_tot_bl","cannwake_bl")

cntr_fnc <- function(var){
  var - mean(var,na.rm=T)
}

df <- df %>%
  dplyr::mutate(across(all_of(vars.standardize),cntr_fnc,.names = "{col}"))

r <- list()

fit_wocov <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~1
)

r[[1]] <- summary(fit_wocov)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (no covars)")
  
fit_wcov <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~ cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[2]] <- summary(fit_wcov)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (with covars)")

fit1 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~timeofday,
    control_formula = ~ cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[3]] <- summary(fit1)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 1")

# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_temp <- df %>% 
  # restrict to interaction A type message and no message
  filter(!(message_type %in% c("B","C"))) %>%
  mutate(interact_A_message = ifelse(actioni==0,0,1))
fit2 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "interact_A_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[4]] <- summary(fit2)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2")

# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_temp <- df %>% 
  # restrict to interaction B type message and no message
  filter(!(message_type %in% c("A","C"))) %>%
  mutate(interact_B_message = ifelse(actioni==0,0,1))

fit2b <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "interact_B_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[5]] <- summary(fit2b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2.2")


# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_temp <- df %>% 
  # restrict to interaction C type message and no message
  filter(!(message_type %in% c("A","B"))) %>%
  mutate(interact_C_message = ifelse(actioni==0,0,1))

fit2c <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "interact_C_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[6]] <- summary(fit2c)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2.3")


df_temp <- df %>% filter(!is.na(prop_awakeuse_prior)) 
fit3 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prop_awakeuse_prior,
    control_formula = ~prop_awakeuse_prior + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[7]] <- summary(fit3)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 3")


fit3b <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_prop_awakeuse_48hrs,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[8]] <- summary(fit3b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 3.2")


fit4 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~wks_since_interv_start,
    control_formula = ~wks_since_interv_start + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[9]] <- summary(fit4)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 4")


fit4b <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~after_day15,
    control_formula = ~after_day15 + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[10]] <- summary(fit4b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 4.2")

fit5 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~week_day_binary,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[11]] <- summary(fit5)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 5")

df_temp <- df %>% filter(!is.na(prior_interv_engag)) 
fit6 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_interv_engag,
    control_formula = ~cov_prop_awakeuse_48hrs + prior_interv_engag  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[12]] <- summary(fit6)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 6")

fit6b <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_interv_engag_72hrs,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[13]] <- summary(fit6b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 6.2")

df_temp <- df %>% filter(!is.na(prior_sent_message)) 
fit7 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_sent_message,
    control_formula = ~prior_sent_message + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[14]] <- summary(fit7)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7")

df_temp <- df %>% filter(!is.na(prior_sent_messages_48hrs)) 
fit7b <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_sent_messages_48hrs,
    control_formula = ~prior_sent_messages_48hrs + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[15]] <- summary(fit7b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7.2")

# short vs no message
df_temp <- df %>%
  # restrict to short message and no message
  filter(message_length!="Long") %>%
  mutate(short_message = ifelse(actioni==0,0,1))

fit8 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "short_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[16]] <- summary(fit8)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 8")


# # long vs no message
df_temp <- df %>%
  # restrict to long message and no message
  filter(message_length!="Short") %>%
  mutate(long_message = ifelse(actioni==0,0,1))

fit8b <- wcls(
    data = df_temp,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "long_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[17]] <- summary(fit8b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 8.2")


fit9 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~male_sex,
    control_formula = ~male_sex + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[18]] <- summary(fit9)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 9")

fit10 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~white_race,
    control_formula = ~white_race + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[19]] <- summary(fit10)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 10")


fit11 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~hispanic_ethn,
    control_formula = ~hispanic_ethn + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[20]] <- summary(fit11)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 11")

fit12 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~canndays_bl,
    control_formula = ~ canndays_bl + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[21]] <- summary(fit12)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 12")

fit12b <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~dsmsc_tot_bl,
    control_formula = ~dsmsc_tot_bl + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[22]] <- summary(fit12b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 12.2")

fit13 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_importance_bl,
    control_formula = ~cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[23]] <- summary(fit13,lincomb = c(1, 1))$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 13")

fit13b <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~high_cann_importance_bl,
    control_formula = ~high_cann_importance_bl + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[24]] <- summary(fit13b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 13.2")

fit13c <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_likely_bl,
    control_formula = ~cann_likely_bl + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[25]] <- summary(fit13c)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 13.3")

fit13d <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_conf_bl,
    control_formula = ~cann_conf_bl + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[26]] <- summary(fit13d)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 13.4")


fit14 <- wcls(
    data = df,
    id = "id",
    outcome = "prop_awakeuse",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~phq2_tot_bl,
    control_formula = ~phq2_tot_bl + cov_prop_awakeuse_48hrs + cov_interv_engag_72hrs  + timeofday + week_day_binary + cann_importance_bl + cannhours_bl + cannwake_bl
)

r[[27]] <- summary(fit14)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14")


res <- r %>% 
  map_df(bind_rows) %>% 
  select(model, everything()) %>%
  dplyr::mutate(model_num = gsub("Moderation Effect Model ","",model),
         model_num = ifelse(model=="Main Effect Model (no covars)","0",
                            ifelse(model=="Main Effect Model (with covars)","0.5",model_num)),
         model_num = as.numeric(model_num)
  )%>%
  dplyr::arrange(model_num) 

# create table with output
res_table <- function(res){
    res %>%
      mutate(term = str_replace(term, "\\(Intercept\\)", "Intercept")) %>%
      rename(Term = term)%>%
      select(-c(model,model_num)) %>%
      kableExtra::kbl(booktabs = TRUE, 
                      longtable = TRUE,
                      digits=3,
                      format = "latex",
                      caption = NULL) %>%
      kableExtra::kable_styling(
        latex_options = c("striped", "hold_position", "repeat_header"),
        font_size = 10
        #full_width = TRUE
      ) %>%
      kableExtra::pack_rows(index = table(fct_inorder(res$model))) %>%
      kableExtra::column_spec(1, width = "6cm") %>%
      kableExtra::column_spec(7, width = "0.5cm") %>%
      kableExtra::column_spec(8, width = "0.5cm") %>%
      kableExtra::footnote(
        general = "baseline cannabis use, and baseline time to cannabis use.", general_title = "", footnote_as_chunk = T
      ) %>%
      kableExtra::footnote(
        general = "prior cannabis use, prior intervention engagement, baseline motivation to change,",
        general_title = "", footnote_as_chunk = T
      )%>%
      kableExtra::footnote(
        general = "Moderation Effect Models include the covariates: time of day, day of week,", general_title = "", footnote_as_chunk = T
      ) %>%
      kableExtra::footnote(
        general = "Notes: Standard errors are not yet adjusted to account for RL uncertainty.", general_title = "", footnote_as_chunk = T
      ) 
}

res_table(res)
```

\newpage

# 2. Primary Aims Analysis (Part 2) with Proximal Intervention Engagement Outcome
    
## *Preliminary* Causal Excursion Effect Estimates
  
**Research Question 3**: Investigate whether, on average, there is a proximal effect of delivering an intervention message on proximal intervention engagement.   
  
**Proximal outcome ($Y_{i,t+1}$)**: Intervention engagement (discrete: 0-3, treated as continuous)  
    
**Treatment indicator ($A_{i,t}$)**: Binary (1=Yes message, 0=No message)  

**Covariates**:  
  
-  time of day – binary (AM=0, PM=1),  
  
-  day of the week – binary (weekday=1, weekend [Fri-Sun]=0),  
  
-  prior intervention engagement – score that ranges from 0-3 averaged over past 6 decision points (i.e., approximately 72 hours), 
  
-  prior human-touch engagement – binary (1=yes, 0=no) for any email, text, or phone call made by study staff (after 72 hours, 120 hours, and 168 hours [1 week])  over past 4 decision points (i.e., approximately 48 hours).  

**Research Question 4**: Explore whether the effect of the intervention message on proximal intervention engagement differs by each of the candidate moderators listed below.  
  
**Candidate Moderators**: 
  
1. *timeofday*: time of day – binary (AM=0, PM=1),
  
2. *prior_interv_engag*: prior intervention engagement – operationalized the same as the proximal outcome, at the prior decision point,
  
- 2.2. *cov_interv_engag_72hrs*: over past 6 decision points,

3. *prop_awakeuse_prior*: prior cannabis use – operationalized the same as the proximal outcome, at the prior decision point,
  
- 3.2. *cov_prop_awakeuse_48hrs*: prior cannabis use over the past 4 decision points,
  
4. *wks_since_interv_start*: time since under treatment (i.e., since intervention start) in weeks,
  
5. *week_day_binary*: day of the week – binary (weekday=1, weekend [Fri-Sun]=0),
  
6. *prior_sent_message*: prior delivery of a message – binary (yes message=1, no message=0), at the prior decision point,
  
- 6.2. *prior_sent_messages_48hrs*: number of messages sent over past 4 decision points,

7. *interact_A_message*: interaction type A message vs. no message – binary (interaction type A message=1, no message=0),  
  
- 7.2. *interact_B_message*: interaction type B message vs. no message – binary (interaction type B message=1, no message=0),  
  
- 7.3. *interact_C_message*: interaction type C message vs. no message – binary (interaction type C message=1, no message=0),
  
8. *short_message*: short message vs. no message – binary (short message=1, no message=0),  
  
- 8.2. *long_message*: long message vs. no message - binary (long message=1, no message=0),  
  
9. *cov_humtch_binary_48hrs*: prior human-touch engagement – binary (1=yes, 0=no) for any email, text, or phone call made by study staff (after 72 hours, 120 hours, and 168 hours [1 week])  over past 4 decision points (i.e., approximately 48 hours),
   
10. *male_sex*: baseline demographic of male biological sex (0=female,1=male),  
  
11. *white_race*: baseline demographic of white race (0=not white, 1=white),   
  
12. *hispanic_ethn*: baseline demographic of hispanic or latino ethnicity (0=not hispanic or latino, 1=hispanic or latino),
  
13. *canndays_bl*: baseline cannabis use severity that is the number of days used cannabis in past month (range: 0-31), which reflects cannabis use frequency, 
  
- 13.2. *dsmsc_tot_bl*: baseline cannabis use severity that is the count of number of symptoms endorsed (range: 0-11), which reflects diagnostic severity,  
  
14. *cann_importance_bl*: baseline motivation to change that is the importance of cutting back cannabis use on a scale from 0 (Not at all) to 10 (Very) at time of baseline survey, and 
  
- 14.2. *high_cann_importance_bl* [a]: baseline motivation to change - binary (0=low motivation to change [score<5], 1=high motivation to change [score>=5]),
  
- 14.3. *cann_likely_bl* [a]: baseline likelihood to change that is how likely one is to cut back cannabis use on a scale from 0 (Not at all) to 10 (Very) at the time of baseline survey,  
  
- 14.4. *cann_conf_bl* [a]: baseline confidence to change that is how confident one is to cut back cannabis use on a scale from 0 (Not at all) to 10 (Very) at the time of baseline survey, 
  
15. *phq2_tot_bl*: baseline mental health, which is the sum across two item scale PHQ-2 ("Over the last two weeks, how often have you been bothered by any of the following problems? Little interest or pleasure in doing things" and "Over the last two weeks, how often have you been bothered by any of the following problems? Feeling down, depressed, or hopeless" with response values of 0=Not at all, 1= Several days, 2=More than half the days, and 3=Nearly every day).

Notes: All continuous candidate moderators are mean-centered.  
[a] This candidate moderator was included after the list of moderators was formalized.

```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(kableExtra)
library(MRTAnalysis)
library(gt)
        
# run with same sample size as for proximal cannabis 
#print(paste0("Sample size: ",nrow(df)))

r <- list()

fit_wocov <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~1
)

r[[1]] <- summary(fit_wocov)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (no covars)")
  
fit_wcov <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~ timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[2]] <- summary(fit_wcov)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (with covars)")


fit1 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~timeofday,
    control_formula = ~ timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[3]] <- summary(fit1)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 1")


df_temp <- df %>% filter(!is.na(prior_interv_engag)) 
fit2 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_interv_engag,
    control_formula = ~timeofday + week_day_binary + prior_interv_engag + cov_humtch_binary_48hrs
)

r[[4]] <- summary(fit2)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2")

fit2b <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_interv_engag_72hrs,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[5]] <- summary(fit2b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2.2")

df_temp <- df %>% filter(!is.na(prop_awakeuse_prior)) 
fit3 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prop_awakeuse_prior,
    control_formula = ~prop_awakeuse_prior + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[6]] <- summary(fit3)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 3")


fit3b <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_prop_awakeuse_48hrs,
    control_formula = ~cov_prop_awakeuse_48hrs + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[7]] <- summary(fit3b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 3.2")


fit4 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~wks_since_interv_start,
    control_formula = ~wks_since_interv_start + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[8]] <- summary(fit4)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 4")

fit5 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~week_day_binary,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[9]] <- summary(fit5)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 5")

df_temp <- df %>% filter(!is.na(prior_sent_message)) 
fit6 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_sent_message,
    control_formula = ~prior_sent_message + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[10]] <- summary(fit7)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 6")

df_temp <- df %>% filter(!is.na(prior_sent_messages_48hrs)) 
fit6b <- wcls(
    data = df_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_sent_messages_48hrs,
    control_formula = ~prior_sent_messages_48hrs + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[11]] <- summary(fit6b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 6.2")


# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_temp <- df %>% 
  # restrict to interaction A type message and no message
  filter(!(message_type %in% c("B","C"))) %>%
  mutate(interact_A_message = ifelse(actioni==0,0,1))
fit7 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "interact_A_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[12]] <- summary(fit7)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7")

# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_temp <- df %>% 
  # restrict to interaction B type message and no message
  filter(!(message_type %in% c("A","C"))) %>%
  mutate(interact_B_message = ifelse(actioni==0,0,1))

fit7b <- wcls(
    data = df_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "interact_B_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[13]] <- summary(fit7b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7.2")


# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_temp <- df %>% 
  # restrict to interaction C type message and no message
  filter(!(message_type %in% c("A","B"))) %>%
  mutate(interact_C_message = ifelse(actioni==0,0,1))

fit7c <- wcls(
    data = df_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "interact_C_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[14]] <- summary(fit7c)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7.3")

# short vs no message
df_temp <- df %>%
  # restrict to short message and no message
  filter(message_length!="Long") %>%
  mutate(short_message = ifelse(actioni==0,0,1))

fit8 <- wcls(
    data = df_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "short_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[15]] <- summary(fit8)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 8")


# # long vs no message
df_temp <- df %>%
  # restrict to long message and no message
  filter(message_length!="Short") %>%
  mutate(long_message = ifelse(actioni==0,0,1))

fit8b <- wcls(
    data = df_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "long_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[16]] <- summary(fit8b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 8.2")

fit9 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_humtch_binary_48hrs,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[17]] <- summary(fit9)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 9")

fit10 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~male_sex,
    control_formula = ~male_sex + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[18]] <- summary(fit10)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 10")

fit11 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~white_race,
    control_formula = ~white_race + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[19]] <- summary(fit11)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 11")


fit12 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~hispanic_ethn,
    control_formula = ~hispanic_ethn + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[20]] <- summary(fit12)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 12")

fit13 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~canndays_bl,
    control_formula = ~ canndays_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[21]] <- summary(fit13)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 13")

fit13b <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~dsmsc_tot_bl,
    control_formula = ~dsmsc_tot_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[22]] <- summary(fit13b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 13.2")

fit14 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_importance_bl,
    control_formula = ~cann_importance_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[23]] <- summary(fit14)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14")

fit14b <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~high_cann_importance_bl,
    control_formula = ~high_cann_importance_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[24]] <- summary(fit14b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14.2")

fit14c <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_likely_bl,
    control_formula = ~cann_likely_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[25]] <- summary(fit14c,lincomb = c(1, 1))$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14.3")

fit14d <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_conf_bl,
    control_formula = ~cann_conf_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[26]] <- summary(fit14d, lincomb = c(1, 1))$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14.4")


fit15 <- wcls(
    data = df,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~phq2_tot_bl,
    control_formula = ~phq2_tot_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[27]] <- summary(fit15)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 15")

res <- r %>% 
  map_df(bind_rows) %>% 
  select(model, everything()) %>%
  dplyr::mutate(model_num = gsub("Moderation Effect Model ","",model),
         model_num = ifelse(model=="Main Effect Model (no covars)","0",
                            ifelse(model=="Main Effect Model (with covars)","0.5",model_num)),
         model_num = as.numeric(model_num)
  )%>%
  dplyr::arrange(model_num) 

# create table with output
res_table <- function(res){
    res %>%
      mutate(term = str_replace(term, "\\(Intercept\\)", "Intercept")) %>%
      rename(Term = term)%>%
      select(-c(model,model_num)) %>%
      kableExtra::kbl(booktabs = TRUE, 
                      longtable = TRUE,
                      digits=3,
                      format = "latex",
                      caption = NULL) %>%
      kableExtra::kable_styling(
        latex_options = c("striped", "hold_position", "repeat_header"),
        font_size = 10
        #full_width = TRUE
      ) %>%
      kableExtra::pack_rows(index = table(fct_inorder(res$model))) %>%
      kableExtra::column_spec(1, width = "6cm") %>%
      kableExtra::column_spec(7, width = "0.5cm") %>%
      kableExtra::column_spec(8, width = "0.5cm") %>%
      kableExtra::footnote(
        general = "prior intervention engagement, and prior human-touch engagement.",
        general_title = "", footnote_as_chunk = T
      )%>%
      kableExtra::footnote(
        general = "Model with covariates adjusts for the following: time of day, day of week,", general_title = "", footnote_as_chunk = T
      ) %>%
      kableExtra::footnote(
        general = "Notes: Standard errors are not yet adjusted to account for RL uncertainty.", general_title = "", footnote_as_chunk = T
      ) 
}

res_table(res)
```

\newpage

Next, we examine the results for proximal intervention enagement when not restricting the sample to decision points with a completed EMA.

```{r, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(kableExtra)
library(MRTAnalysis)
library(gt)

# run with sample size that reflects only missingness in proximal intervention engagement
df_engag <- full_dat %>%
  # restrict to participants with at least 3 completed EMAs
  dplyr::filter(num_emas_l >= 3) %>%
  # remove observations where the randomization information is missing
  dplyr::filter(missing_rand != 1) %>%
  dplyr::filter(!is.na(interv_engagement_l))

#print(paste0("Common Sample Size: ",nrow(df)))
#print(paste0("Engagement Sample Size: ",nrow(df_engag)))


r <- list()

fit_wocov_b <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~1
)


r[[1]] <- summary(fit_wocov_b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (no covars)")

fit_wcov_b <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~ timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[2]] <- summary(fit_wcov_b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Main Effect Model (with covars)")


fit1 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~timeofday,
    control_formula = ~ timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[3]] <- summary(fit1)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 1")


df_engag_temp <- df_engag %>% filter(!is.na(prior_interv_engag)) 
fit2 <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_interv_engag,
    control_formula = ~timeofday + week_day_binary + prior_interv_engag + cov_humtch_binary_48hrs
)

r[[4]] <- summary(fit2)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2")

fit2b <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_interv_engag_72hrs,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[5]] <- summary(fit2b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 2.2")

df_engag_temp <- df_engag %>% filter(!is.na(prop_awakeuse_prior))
fit3 <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prop_awakeuse_prior,
    control_formula = ~prop_awakeuse_prior + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[6]] <- summary(fit3)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 3")

df_engag_temp <- df_engag %>% filter(!is.na(cov_prop_awakeuse_48hrs))
fit3b <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_prop_awakeuse_48hrs,
    control_formula = ~cov_prop_awakeuse_48hrs + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[7]] <- summary(fit3b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 3.2")


fit4 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~wks_since_interv_start,
    control_formula = ~wks_since_interv_start + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[8]] <- summary(fit4)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 4")

fit5 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~week_day_binary,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[9]] <- summary(fit5)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 5")

df_engag_temp <- df_engag %>% filter(!is.na(prior_sent_message))
fit6 <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_sent_message,
    control_formula = ~prior_sent_message + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[10]] <- summary(fit7)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 6")

df_engag_temp <- df_engag %>% filter(!is.na(prior_sent_messages_48hrs))
fit6b <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~prior_sent_messages_48hrs,
    control_formula = ~prior_sent_messages_48hrs + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[11]] <- summary(fit6b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 6.2")


# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_engag_temp <- df_engag %>%
  # restrict to interaction A type message and no message
  filter(!(message_type %in% c("B","C"))) %>%
  mutate(interact_A_message = ifelse(actioni==0,0,1))
fit7 <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "interact_A_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[12]] <- summary(fit7)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7")

# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_engag_temp <- df_engag %>%
  # restrict to interaction B type message and no message
  filter(!(message_type %in% c("A","C"))) %>%
  mutate(interact_B_message = ifelse(actioni==0,0,1))

fit7b <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "interact_B_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[13]] <- summary(fit7b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7.2")


# type of interaction (A, B or C) – categorical (A=0, B=1, C=2)
df_engag_temp <- df_engag %>%
  # restrict to interaction C type message and no message
  filter(!(message_type %in% c("A","B"))) %>%
  mutate(interact_C_message = ifelse(actioni==0,0,1))

fit7c <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "interact_C_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[14]] <- summary(fit7c)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 7.3")

# short vs no message
df_engag_temp <- df_engag %>%
  # restrict to short message and no message
  filter(message_length!="Long") %>%
  mutate(short_message = ifelse(actioni==0,0,1))

fit8 <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "short_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[15]] <- summary(fit8)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 8")


# # long vs no message
df_engag_temp <- df_engag %>%
  # restrict to long message and no message
  filter(message_length!="Short") %>%
  mutate(long_message = ifelse(actioni==0,0,1))

fit8b <- wcls(
    data = df_engag_temp,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "long_message",
    rand_prob = "probi",
    moderator_formula = ~1,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[16]] <- summary(fit8b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 8.2")

fit9 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cov_humtch_binary_48hrs,
    control_formula = ~timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[17]] <- summary(fit9)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 9")

fit10 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~male_sex,
    control_formula = ~male_sex + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[18]] <- summary(fit10)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 10")

fit11 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~white_race,
    control_formula = ~white_race + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[19]] <- summary(fit11)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 11")


fit12 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~hispanic_ethn,
    control_formula = ~hispanic_ethn + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[20]] <- summary(fit12)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 12")

fit13 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~canndays_bl,
    control_formula = ~ canndays_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[21]] <- summary(fit13)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 13")

fit13b <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~dsmsc_tot_bl,
    control_formula = ~dsmsc_tot_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[22]] <- summary(fit13b,lincomb = c(1, 1))$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 13.2")

fit14 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_importance_bl,
    control_formula = ~cann_importance_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[23]] <- summary(fit14)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14")

fit14b <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~high_cann_importance_bl,
    control_formula = ~high_cann_importance_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[24]] <- summary(fit14b)$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14.2")

fit14c <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_likely_bl,
    control_formula = ~cann_likely_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[25]] <- summary(fit14c,lincomb = c(1, 1))$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14.3")

fit14d <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~cann_conf_bl,
    control_formula = ~cann_conf_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[26]] <- summary(fit14d,lincomb = c(1, 1))$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 14.4")


fit15 <- wcls(
    data = df_engag,
    id = "id",
    outcome = "interv_engagement_l",
    treatment = "actioni",
    rand_prob = "probi",
    moderator_formula = ~phq2_tot_bl,
    control_formula = ~phq2_tot_bl + timeofday + week_day_binary + cov_interv_engag_72hrs + cov_humtch_binary_48hrs
)

r[[27]] <- summary(fit15,lincomb = c(1, 1))$causal_excursion_effect %>% as_tibble(rownames = "term") %>%
  mutate(model="Moderation Effect Model 15")

res <- r %>% 
  map_df(bind_rows) %>% 
  select(model, everything()) %>%
  dplyr::mutate(model_num = gsub("Moderation Effect Model ","",model),
         model_num = ifelse(model=="Main Effect Model (no covars)","0",
                            ifelse(model=="Main Effect Model (with covars)","0.5",model_num)),
         model_num = as.numeric(model_num)
  )%>%
  dplyr::arrange(model_num) 

# create table with output
res_table <- function(res){
    res %>%
      mutate(term = str_replace(term, "\\(Intercept\\)", "Intercept")) %>%
      rename(Term = term)%>%
      select(-c(model,model_num)) %>%
      kableExtra::kbl(booktabs = TRUE, 
                      longtable = TRUE,
                      digits=3,
                      format = "latex",
                      caption = NULL) %>%
      kableExtra::kable_styling(
        latex_options = c("striped", "hold_position", "repeat_header"),
        font_size = 10
        #full_width = TRUE
      ) %>%
      kableExtra::pack_rows(index = table(fct_inorder(res$model))) %>%
      kableExtra::column_spec(1, width = "6cm") %>%
      kableExtra::column_spec(7, width = "0.5cm") %>%
      kableExtra::column_spec(8, width = "0.5cm") %>%
      kableExtra::footnote(
        general = "prior intervention engagement, and prior human-touch engagement.",
        general_title = "", footnote_as_chunk = T
      )%>%
      kableExtra::footnote(
        general = "Model with covariates adjusts for the following: time of day, day of week,", general_title = "", footnote_as_chunk = T
      ) %>%
      kableExtra::footnote(
        general = "Notes: Standard errors are not yet adjusted to account for RL uncertainty.", general_title = "", footnote_as_chunk = T
      ) 
}

res_table(res)
```
\newpage

# 3. Draft Interpretation of Results

Below we include interpretations of the results from the four research questions (RQ1-RQ4), as outlined above.  
\vspace{5pt}
  
For **RQ1**, the average proximal effect of prompting (vs. not prompting) with a message on proximal cannabis use (proportion of waking hours using cannabis 0-1, treated as continuous) was not significantly different from the null of zero (b=0.009; 95% CI: -0.003, 0.020; p-value=0.134). Herein, we adjust for the following covariates for noise reduction: time of day, day of week, prior cannabis use, prior intervention engagement, baseline motivation to change, baseline cannabis use, and baseline time to cannabis use.
\vspace{5pt}
  
For **RQ2** with respect to proximal cannabis use, only the interaction between prompting with a message and baseline motivation to change (scale: 0 (not at all)-10 (very) and centered at grand mean) was significantly different from zero (b=-0.005; 95% CI: -0.010, -0.001; p-value=0.030).   
  
- This indicates that prompting with an intervention message is less adverse for proximal cannabis use, with a 1 unit increase in importance to cut back cannabis use, as self-reported at time of baseline survey, from the mean. For participants with a 1 unit increase in baseline cannabis motivation to change from the mean, prompting with an intervention message increases proximal cannabis use by 0.003, as compared to a 0.009 increase in the same for participants with mean motivation to change. However, we caution against resolute interpretation of this effect, considering the remainder of the tests for RQ2 demonstrated null results. 
\vspace{5pt} 
  
For **RQ3** - **RQ4**, we report the results for the second version without restricting the analysis dataset to EMA completions. This is because EMA completion was a component of the construction of the intervention engagement proximal outcome. For **RQ3**, we similarly find that the effect of prompting (vs. not prompting) with a message on proximal intervention engagement (scale: 0-3, treated as continuous) was not significantly different from the null of zero (b=-0.030; 95% CI: -0.075, 0.015; p-value=0.190). The following precision covariates are included: time of day, day of week, prior intervention engagement, and prior human-touch engagement.  
\vspace{5pt}
  
For **RQ4** with respect to proximal intervention engagement, the following candidate moderators bore a significant difference on the effect of a message on engagement: baseline cannabis use severity (count of symptoms endorsed and ranges from 0-11), baseline likelihood to cut back on cannabis use (0 [not at all]-10 [very]), baseline confidence in cutting back on cannabis use (0 [not at all]-10 [very]), and baseline mental health (sum of two item scale and ranges from 0-6).
  
  